\chapter*{ACKNOWLEDGEMENT}
    \def\baselinestretch{1.0}
    \par\textsl{I am deeply grateful to Rev. Fr. (Dr.) Stephen Mavely, the Founder Vice-Chancellor of Assam Don Bosco University, whose unwavering belief in me has been a source of immense encouragement. I owe him my sincere thanks for choosing to appoint me as an Assistant Professor in the Department of Physics over more qualified candidates. Throughout my association with ADBU, he has consistently taken a keen interest in the progress of my research, for which I am profoundly thankful.}
    
    \par\textsl{I extend my heartfelt thanks to the Vice-Chancellor of Assam Don Bosco University, Rev. Fr. Jose Palely, for his promptness and support in ensuring that every process has been smooth and hassle-free during my journey.}
    
    \par\textsl{I am equally thankful to Prof. Jai Narayan Vishwakarma, Director of Research at Assam Don Bosco University, for creating and sustaining a healthy research atmosphere at the university. His availability and willingness to address any concerns have been instrumental in my progress, and his appreciation for my efforts has meant a great deal to me.}
    
    \par\textsl{My deepest gratitude goes to my research supervisor, Dr. Monmoyuri Baruah, whose commitment to my academic growth has been unmatched. She has always ensured that I have access to the necessary research facilities at IUCAA, Pune, while placing me on a path that both challenges and nurtures my potential.}
    
    \par\textsl{I also wish to sincerely thank Prof. Ranjeev Misra, Scientist-G at IUCAA, Pune, and my research co-supervisor, for his invaluable guidance during my visits to Pune. His support and introductions to numerous experts have helped me overcome challenges and move forward in my research.}
    
    \par\textsl{I will forever cherish the inspiration I have received from Dr. Basil Koikara, the Founder Registrar of Assam Don Bosco University, Rev. Fr. Joseph Nellanat, the Pro-Vice-Chancellor of Assam Don Bosco University, and Rev. Fr. Biju Michael, former Registrar of Assam Don Bosco University. Their leadership and dedication have left a lasting impact on me.}

    \newpage
    \par\textsl{I am deeply thankful to my colleagues at ADBU for their constant encouragement and belief in me. A special mention goes to Dr. Samrat Dey, Dr. Ngangom Aomoa, Dr. Debajyoti Dutta, Mr. Dipjyoti Sarma, Dr. Kaustubh Bhattacharyya, Dr. Pratikshya Bezbaruah, Dr. Sumita K. Sharma, Dr. Aibanjop Pyngrope, Dr. Bikash Borah, Dr. Indrani Dakua, Dr. C. Satyananda Singh, Dr. Yajnya Sapkota, Dr. Nazneen Hussain, Dr. Eliyash Ahmed, Ms. Nairika Deka, Mr. Ankon Borah, Mr. Deepjyoti Mahanta, and Mr. Mintu Hazarika. Your friendship and encouragement have played a crucial role in my journey.}
    
    \par\textsl{I would also like to express my sincere gratitude to all the researchers and scholars whose work I have cited throughout this thesis. Their contributions have laid the foundation for my own research and have been a guiding light in shaping my understanding of this field. The collective wisdom embedded in their writings has inspired and enriched my work, and I am deeply indebted to them for their insights, methodologies, and discoveries, which have propelled the advancement of knowledge across generations.}
    
    \par\textsl{I must also acknowledge all of my students over the past decade, whose curiosity and enthusiasm have been infectious and have continuously inspired me.}
    
    \par\textsl{Finally, my deepest gratitude is reserved for my family, who hold the most special place in this journey. Their unwavering love, patience, and support have been the bedrock upon which this entire endeavour has rested. Their quiet resilience and faith in me have fuelled my determination. This thesis is as much a testament to their support as it is to my efforts.}
    
    \bigskip\medskip
    \bigskip\medskip
    \bigskip\medskip\bigskip\medskip
    \noindent\\
    \hfill (\authorname)
    \noindent\\
    \hfill {\submissiontime} \\
    \hfill Department of \department\\
    \hfill \university.