\chapter{Bio-data of the Scholar} \label{appendix:biodata}

    \textbf{Name:} \authorname
    
    \textbf{Gender:} Male
    
    \textbf{Father’s name:} Late Surendranath Bhattacharya
    
    \textbf{Mother’s name:} Labanyamoyee Bhattacharya
    
    \textbf{Present address:} Department of Physics, Rangapara College, Rangapara, Dist. Sonitpur, Assam -- 784 505.
    
    \textbf{Home address:} House Ho. 3, Byelane Mathura Boro Path, Nagarik Path, Chandan Nagar, Ghoramara, P.O. Beltola, P.S. Hatigaon, Guwahati, Dist. Kamrup (M), Assam -- 781 028.
    
    \textbf{Nationality:} Indian
    
    \textbf{Date of Birth:} 25 February, 1984
    
    \textbf{Age on 1st January 2024:} 39 years
    
    \textbf{Educational Qualifications:} M.Sc. (Physics), M.Tech. (Applied Optics), SLET
    
    \textbf{Service Experience:} \vspace{-3ex}
    \begin{enumerate}
    	\item \textit{Assistant Professor}, {Department of Physics}, {Rangapara College}, {Rangapara, Dist. Sonitpur, Assam}. {24 Sep. 2022 -- present}
    	\item \textit{Assistant Professor}, {Department of Physics}, {Assam Don Bosco University}, {Tapesia Gardens, Sonapur, Assam}. {6 Jul. 2015 -- 23 Sep. 2022}
    	\item \textit{Faculty (Physics)}, {Concept Educations}, {Guwahati, Dist. Kamrup (M), Assam}. {6 Jun. 2013 -- 4 Jul. 2015}
    	\item \textit{Faculty (Physics)}, {Aakash Institute}, {Guwahati, Dist. Kamrup (M), Assam}. {19 Oct. 2012 -- 31 May 2013}
    	\item \textit{PGT (Physics)}, {Delhi Public School Guwahati}, {Guwahati, Dist. Kamrup (M), Assam}. {4 Jan. 2012 -- 18 Oct. 2012}
    	\item \textit{Guest Faculty}, {Gauhati University}, {Guwahati, Dist. Kamrup (M), Assam}. {2 Jan. 2012 -- 31 Dec. 2012}
    	\item \textit{Engineer -- Product Verification}, {Tejas Networks Ltd.}, {Bangalore, Dist. Bangalore Urban, Karnataka}. {16 Mar. 2011 -- 9 Dec. 2011}
    	%\item {Engineer -- Product Verification}, {Tejas Networks Ltd.}, {# 58, 1st Main Road, J.P. Nagar 3rd Phase, Bangalore}. {16 Mar. 2011 -- 9 Dec. 2011}
    	\item \textit{Sub Area Manager}, {Reliance Communications Limited}, {Guwahati, Dist. Kamrup (M), Assam}. {2 Nov. 2009 -- 12 Mar. 2011}
    \end{enumerate}